The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-28 paper/sections/methods.tex
update distance weight plot caption
fixed typo in equation

%%single projector for every object
When assembled for all parts,~\refeq{hfit}, yields a block upper triangular matrix $U$ and a sparse matrix $B$ ~(\reffig{multiparts}) which can be used to efficiently to compute the projection 
operator for the entire object $\Pi = U^{-1}B\vc{q}$. 
The structure of $U$ and $B$ ensures that $\Pi$ only couples objects which share deformation centers, which implies a sparse $\Pi$. 
The per-part projection operators $\Pi_i$ correspond to blocks of rows of $\Pi$. 
Coupling via the deformation origins ensures our method will reproduce rigid and linear deformations in regions around these points, while higher order 
terms help compensate for more local deformations.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.33in]{figures/plot_distance_weight_both.pdf}
    \caption{Distance weight as a function of primary and total ray length with cutoff distance 50 (left). Here we use different colors to denote different parts (right).}
    % \caption{We plot the distance weight with respect to the primary and total ray length. Here the cutoff distance is 50.
    % }
    \label{fig:plot_distance_weight}
    \vspace{-5pt}
\end{figure}

@@

\dave{Ty: a bit more here, show the transformation of the integral via divergence theorem then show the final discrete version. Clearly define the quadrature rules.}
The key idea behind raycasting quadrature is to transform a domain integral of the form $I=\int_{\Omega} f(X,Y,Z) d\Omega$ to an easier form that enables us to select quadrature points in an entirely meshless manner. The first transformation is to convert the domain of the integral to an \textit{auxiliary domain}, $\Omega_R$ on which integration is easy to compute. In our case we take this domain to be an axis-aligned bounding box around our model, and rewrite integration as $I=\int_{\Omega_R} g(X,Y,Z) d\Omega_R$ where $g$ evaluates to zero outside of $\Omega$, but equals $f$ inside $\Omega$. Next we apply the Divergence theorem to rewrite our integral as
\newcommand{\Zeta}{\mathrm{Z}}
\begin{equation}
\int_{\Omega_R} g(X,Y,Z) d\Omega_R = \int_{\Gamma_R}\left(\int_{X_1}^{X_2} g(\alpha, Y, Z) d\alpha)\right)\mathbf{n} d\Gamma.
\end{equation}
where $\Gamma_R$ is the boundary of the bounding box with normals $\mathbf{n}$ and $X_1$ and $X_2$ represent the minimum and maximum values of the box along the $x$-axis. With this form, all we require to evaluate the outer integral is to integrate over the $y$-$z$ plane located at $X_1$. With this simple form, the normal term may be excluded as it always equals $1$ \dave{isn;t it a vector $(1,0,0)$ or something like that ? }in the case of an axis-aligned bounding box. Finally, raycasting is used to evaluate the line integral along the x-axis. From here, we find all the intersection intervals where the ray is inside $\Omega$, and select quadrature points uniformly along this interval. Thus, this transformation from the original volume integral into an integral over a $y$-$z$ plane plus axis-aligned rays enables us to integrate the volumes of our NURBS models in a completely meshless approach.

>>>>

%%single projector for every object
When assembled for all parts,~\refeq{hfit}, yields a block upper triangular matrix $U$ and a sparse matrix $B$ ~(\reffig{multiparts}) which can be used to efficiently to compute the projection 
operator for the entire object $\Pi = U^{-1}B$. 
The structure of $U$ and $B$ ensures that $\Pi$ only couples objects which share deformation centers, which implies a sparse $\Pi$. 
The per-part projection operators $\Pi_i$ correspond to blocks of rows of $\Pi$. 
Coupling via the deformation origins ensures our method will reproduce rigid and linear deformations in regions around these points, while higher order 
terms help compensate for more local deformations.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.33in]{figures/plot_distance_weight_both.pdf}
    \caption{Distance weight as a function of primary ray length $d_{\text{primary}}$ and total ray length $d_{\text{total}}$ with cutoff distance 50 (left). Here we use different colors to denote different parts (right).}
    % \caption{We plot the distance weight with respect to the primary and total ray length. Here the cutoff distance is 50.
    % }
    \label{fig:plot_distance_weight}
    \vspace{-5pt}
\end{figure}

@@

\dave{Ty: a bit more here, show the transformation of the integral via divergence theorem then show the final discrete version. Clearly define the quadrature rules.}
The key idea behind raycasting quadrature is to transform a domain integral of the form $I=\int_{\Omega} f(X,Y,Z) d\Omega$ to an easier form that enables us to select quadrature points in an entirely meshless manner. The first transformation is to convert the domain of the integral to an \textit{auxiliary domain}, $\Omega_R$ on which integration is easy to compute. In our case we take this domain to be an axis-aligned bounding box around our model, and rewrite integration as $I=\int_{\Omega_R} g(X,Y,Z) d\Omega_R$ where $g$ evaluates to zero outside of $\Omega$, but equals $f$ inside $\Omega$. Next we apply the Divergence theorem to rewrite our integral as
\newcommand{\Zeta}{\mathrm{Z}}
\begin{equation}
\int_{\Omega_R} g(X,Y,Z) d\Omega_R = \int_{\Gamma_R}\left(\int_{X_1}^{X_2} g(\alpha, Y, Z) d\alpha)\right)\mathbf{n} d\Gamma_R.
\end{equation}
where $\Gamma_R$ is the boundary of the bounding box with normals $\mathbf{n}$ and $X_1$ and $X_2$ represent the minimum and maximum values of the box along the $x$-axis. With this form, all we require to evaluate the outer integral is to integrate over the $y$-$z$ plane located at $X_1$. With this simple form, the normal term may be excluded as it always equals $1$ \dave{isn;t it a vector $(1,0,0)$ or something like that ? }in the case of an axis-aligned bounding box. Finally, raycasting is used to evaluate the line integral along the x-axis. From here, we find all the intersection intervals where the ray is inside $\Omega$, and select quadrature points uniformly along this interval. Thus, this transformation from the original volume integral into an integral over a $y$-$z$ plane plus axis-aligned rays enables us to integrate the volumes of our NURBS models in a completely meshless approach.
